No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-20 main/LICS.tex
the phenomenal parity proof included

Equivalence in this fragment is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are generally not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.

These characteristics carry over to the full fragment, including the par.
%
They hold the following lessons on rewiring for the design of our encoding in Section~\ref{sec:encoding}. 
%
Firstly, making proof nets equivalent is generally easier than preventing them from being equivalent, and in particular changing a formula $A$ to $A\tn\bot$ dramatically increases its rewiring potential.
%
The focus of our encoding will therefore be on preventing undesired linkings from being proof nets at all, rather than being unreachable by rewiring.
%
Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding, and should be no more than a technical distraction.

@@

>>>>

\subsection*{Parity}

We shall associate a \emph{parity} with any two linkings $\links$ and $\links'$ of the same sequent $\Gamma$. We shall find that the parity of equivalent linkings is always even; and that the converse holds when $\Gamma$ is a 1-alternation sequent.

For this argument we shall assume that the connectives $\tn$ and $\parr$ are n-ary, and that every argument of a $\tn$ is a $\parr$ and vice versa. Assume also that $\Gamma$ consists of a single formula, if necessary by introducing a $\parr$ at the root. Now fix an arbitrary switching of $\Gamma$; this switching together with a linking $\links$ defines a tree whose vertices are the subformulae of $\Gamma$ and whose edges are the edges of the chosen switching together with the links of $\links$. Take the root of the formula $\Gamma$ to be the root of this tree. Now consider the edges of the tree to be directed away from the root; so the root has in-degree $0$ and the other vertices have in-degree $1$. This therefore establishes a bijection between the edges of the tree and the non-root vertices.
%
A second linking $\links'$ similarly establishes such a bijection. Given both linkings $\links$ and $\links'$, we compose these bijections to obtain a permutation of the proper subformulae of $\Gamma$. Finally the parity of the pair of linkings is taken to be the parity of this permutation.

\begin{lemma}
	The parity is well-defined, in the sense that it does not depend on the choice of switching.
\end{lemma}
\begin{IEEEproof}
	It suffices to show that changing the switching of a single $\parr$ node does not change the parity.
	Observe that the tree is bipartite: every edge connects a $\tn$ with a $\parr$ node. Therefore two
	arguments of a $\parr$ are connected, in the tree, by a path of even length. Changing the switching will
	therefore induce a cyclic permutation of an odd number of edges (the even number of edges on the path
	connecting the two $\parr$ arguments, and the edge connecting the $\parr$ to its argument); and a cyclic
	permutation of an odd number of elements is an even permutation.
\end{IEEEproof}

Essentially the same argument also establishes that:
\begin{lemma}
	If two linkings are equivalent, their parity is even.
\end{lemma}

\begin{proposition}
\label{prop:parity determines equivalence}
Two proof nets for a basic sequent with at least two tensor-formulae are equivalent if and only if they have the same parity.
\end{proposition}

\begin{IEEEproof}
By Proposition~\ref{prop:level0 max binary} the sequent has at most 2 equivalence classes.
%
Given two proof nets of even parity, both must be in the other equivalence class than a proof net with odd relative parity to both, which exists by exchanging two jumps from one tensor-formula.
\end{IEEEproof}

The previous illustrates that equivalence in the fragment without $\parr$ is determined by two main characteristics: 1) proof nets that differ by the exchange of exactly two links are generally not equivalent; and 2) as long as there are at least two tensor-formulae in the sequent, proof nets are equivalent whenever this is possible while respecting the previous.

These characteristics hold the following lessons on rewiring for the design of our encoding in Section~\ref{sec:encoding}. 
%
Firstly, making proof nets equivalent is generally easier than preventing them from being equivalent, and in particular changing a formula $A$ to $A\tn\bot$ dramatically increases its rewiring potential.
%
The focus of our encoding will therefore be on preventing undesired linkings from being proof nets at all, rather than being unreachable by rewiring.
%
Secondly, the problem that proof nets up to a single exchange of links are generally not equivalent is too subtle to be useful as a feature of an encoding, and shall mean no more than a technical distraction.

@@

%% WORKING HERE

%We shall translate a pair of
